# Research Question 3

**Is perceived social support received from Facebook (fmssSubscore) associated with health service utilization?**

* Among participants with positive screens for psychiatric disorders or suicidal ideation?
* Among all participants?

Use interaction terms to examine effect modification by positive screens for
psychiatric disorders or suicidal ideation.
**Look at the unadjusted and adjusted odds ratio for the `fmssSubscore` term.**

## Unadjusted comparisons

```{r}
align <- "llcccccc"
digits <- c(0, 0, 1, 1, 0, 0, 0, 0)
df0 %>% means2Group("fmssSubscore", "indVANeverEnrolled") %>% kable(align = align, digits = digits)
```

\newline

```{r}
df0 %>% means2Group("fmssSubscore", "indVANotUse12mo") %>% kable(align = align, digits = digits)
```

\newline

```{r plot2GroupsRQ3}
df0 %>% 
  select(record_id, fmssSubscore, indVANeverEnrolled, indVANotUse12mo) %>% 
  gather(key = variable, value = value, -record_id, -fmssSubscore) %>% 
  filter(!is.na(value) & !is.na(fmssSubscore)) %>% 
  mutate(variable = case_when(variable == "indVANeverEnrolled" ~ "Never enrolled in VA",
                              variable == "indVANotUse12mo" ~ "Did not use VA health services\nin prior 12 months")) %>% 
  mutate(variable = factor(variable, levels = c("Never enrolled in VA", "Did not use VA health services\nin prior 12 months"))) %>% 
  mutate(value = factor(value, levels = c(FALSE, TRUE), labels = c("No", "Yes"))) %>% 
  ggplot() +
  ggtitle("Psychiatric symptoms by\nModified Facebook Measure of Social Support") +
  aes(x = value, y = fmssSubscore, color = value, fill = value) +
  geom_violin(alpha = 1/1) +
  scale_x_discrete("") +
  scale_y_continuous("FMSS subscore (FMSS items 1 + 2 + 3)") +
  scale_color_brewer(palette = "Set1") + 
  scale_fill_brewer(palette = "Set1") +
  facet_wrap(~ variable) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5))
```


## Adjusted comparisons

```{r}
x <- "fmssSubscore"
covarDemog <- c("age", "gender", "race", "hispanic", "marital2")
covarPsySoc <- c("countSocialMediaExclFB",
                 "comm_inperson",
                 "indSuicideConsideredEver",
                 "countSuicideAttempts")
```

Filter subjects with missing covariates.

```{r}
df3 <-
  df0 %>% 
  select_at(c("record_id", covarDemog, covarPsySoc)) %>% 
  na.omit() %>% 
  select(record_id) %>% 
  merge(., df0, by = "record_id")
```

Set modeling covariates.

```{r}
covar <- c(covarDemog, covarPsySoc)
covar
```

### Never enrolled in VA

```{r}
y <- "indVANeverEnrolled"
```

**PC-PTSD**

```{r}
z <- "indNotPTSD"
```

```{r}
M0 <- fitModel(df3, y, x, int = z)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df3, y, x, int = z, covar = covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```

**PHQ-2**

```{r}
z <- "indNotPHQ"
```

```{r}
M0 <- fitModel(df3, y, x, int = z)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df3, y, x, int = z, covar = covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```

**AUDIT-C**

```{r}
z <- "indNotAuditC"
```

```{r}
M0 <- fitModel(df3, y, x, int = z)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df3, y, x, int = z, covar = covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```

**DSI-SS**

```{r}
z <- "indNotDSISS"
```

```{r}
M0 <- fitModel(df3, y, x, int = z)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df3, y, x, int = z, covar = covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```


### Did not use VA health services in prior 12 months

```{r}
y <- "indVANotUse12mo"
```

**PC-PTSD**

```{r}
z <- "indNotPTSD"
```

```{r}
M0 <- fitModel(df3, y, x, int = z)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df3, y, x, int = z, covar = covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```

**PHQ-2**

```{r}
z <- "indNotPHQ"
```

```{r}
M0 <- fitModel(df3, y, x, int = z)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df3, y, x, int = z, covar = covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```

**AUDIT-C**

```{r}
z <- "indNotAuditC"
```

```{r}
M0 <- fitModel(df3, y, x, int = z)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df3, y, x, int = z, covar = covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```

**DSI-SS**

```{r}
z <- "indNotDSISS"
```

```{r}
M0 <- fitModel(df3, y, x, int = z)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df3, y, x, int = z, covar = covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```
