# Research Question 1

**Is perceived social support received from Facebook (FMSS) associated with lower rates of**

* Positive screens for psychiatric disorders
  * PC-PTSD
  * PHQ-2
  * AUDIT-C
* Positive screen for suicidality?
  * DSI-SS


## Unadjusted comparisons

```{r}
align <- "llcccccc"
digits <- c(0, 0, 1, 1, 0, 0, 0, 0)
df0 %>% means2Group("fmss", "indPTSD") %>% kable(align = align, digits = digits)
```

\newline

```{r}
df0 %>% means2Group("fmss", "indPHQ") %>% kable(align = align, digits = digits)
```

\newline

```{r}
df0 %>% means2Group("fmss", "indAuditC") %>% kable(align = align, digits = digits)
```

\newline

```{r}
df0 %>% means2Group("fmss", "indDSISS") %>% kable(align = align, digits = digits)
```

\newline

```{r plot2GroupsRQ1}
df0 %>% 
  select(record_id, fmss, indPTSD, indPHQ, indAuditC, indDSISS) %>% 
  gather(key = variable, value = value, -record_id, -fmss) %>% 
  filter(!is.na(value) & !is.na(fmss)) %>% 
  mutate(variable = case_when(variable == "indPTSD" ~ "PC-PTSD",
                              variable == "indPHQ" ~ "PHQ-2",
                              variable == "indAuditC" ~ "AUDIT-C",
                              variable == "indDSISS" ~ "DSI-SS")) %>% 
  mutate(variable = factor(variable, levels = c("PC-PTSD", "PHQ-2", "AUDIT-C", "DSI-SS"))) %>% 
  mutate(value = factor(value, levels = c(FALSE, TRUE), labels = c("Negative", "Positive"))) %>% 
  ggplot() +
  ggtitle("Psychiatric symptoms by\nModified Facebook Measure of Social Support") +
  aes(x = value, y = fmss, color = value, fill = value) +
  geom_violin(alpha = 1/1) +
  scale_x_discrete("") +
  scale_y_continuous("FMSS") +
  scale_color_brewer(palette = "Set1") + 
  scale_fill_brewer(palette = "Set1") +
  facet_wrap(~ variable) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5))
```


## Adjusted comparisons

```{r}
x <- "fmss"
covar <- c("countSocialMediaExclFB",
           "comm_inperson",
           "indSuicideConsideredEver",
           "countSuicideAttempts")
```

Filter subjects with missing covariates.

```{r}
df1 <-
  df0 %>% 
  select_at(c("record_id", covar)) %>% 
  na.omit() %>% 
  select(record_id) %>% 
  merge(., df0, by = "record_id")
```


### PC-PTSD

```{r}
y <- "indPTSD"
M0 <- fitModel(df1, y, x)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df1, y, x, covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```

```{r}
beta <- M[["modelObject"]][["coefficients"]][[x]]
delta <- 10
```

For a `r delta`-point increase in FMSS, the adjusted odds ratio is `r sprintf("%.03f", exp(beta * delta))`.


### PHQ-2

```{r}
y <- "indPHQ"
M0 <- fitModel(df1, y, x)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df1, y, x, covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```

```{r}
beta <- M[["modelObject"]][["coefficients"]][[x]]
delta <- 10
```

For a `r delta`-point increase in FMSS, the adjusted odds ratio is `r sprintf("%.03f", exp(beta * delta))`.

### AUDIT-C

```{r}
y <- "indAuditC"
M0 <- fitModel(df1, y, x)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df1, y, x, covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```

```{r}
beta <- M[["modelObject"]][["coefficients"]][[x]]
delta <- 10
```

For a `r delta`-point increase in FMSS, the adjusted odds ratio is `r sprintf("%.03f", exp(beta * delta))`.


### DSI-SS

```{r}
y <- "indDSISS"
M0 <- fitModel(df1, y, x)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df1, y, x, covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```

```{r}
beta <- M[["modelObject"]][["coefficients"]][[x]]
delta <- 10
```

For a `r delta`-point increase in FMSS, the adjusted odds ratio is `r sprintf("%.03f", exp(beta * delta))`.


## Additional questions

> Some issues that additional analysis could clarify is whether people have a
> tendency to substitute social contact on social media for in-person social
> contact, and whether that substitution is bad for your emotional well-being.
> It would be interesting to look at:
> 
> * Do people who spend a lot of time (or frequently use) Facebook spend less
>   time meeting up in-person (i.e., possibly substitute one form of social
>   contact for another)? Variables: `comm_facebook`, `fb_freq`, `comm_inperson`
> * Do people who spend a lot of time (or frequently use) Facebook and spend
>   less time in-person have higher risk for psychiatric disorders?

```{r, warning = FALSE}
df2 <- 
  df0 %>% 
  mutate(comm_facebook = factor(comm_facebook,
                                levels = c("Every few weeks or less often", 
                                           "Once a week", 
                                           "A few times a week", 
                                           "Once a day", 
                                           "Several times a day"),
                                labels = c(rep("Less than daily", 3), 
                                           rep("Daily or more", 2))),
         fb_freq = factor(fb_freq,
                          levels = c("Never",
                                     "Every few weeks", 
                                     "Once a week", 
                                     "A few times a week", 
                                     "Once a day", 
                                     "Several times a day"),
                          labels = c(rep("Less than daily", 4), 
                                     rep("Daily or more", 2))),
         comm_inperson = factor(comm_inperson,
                                levels = c("Every few weeks or less often",
                                           "Once a week",
                                           "A few times a week",
                                           "Once a day",
                                           "Several times a day"),
                                labels = c(rep("Less than daily", 3),
                                           rep("Daily or more", 2)))) %>% 
  mutate(comm_facebook = droplevels(comm_facebook),
         fb_freq = droplevels(fb_freq),
         comm_inperson = droplevels(comm_inperson))
varlabel <- data.frame(name = c("comm_inperson", "comm_facebook", "fb_freq"),
                       label = c("Meet up in-person",
                                 "Actively interact on Facebook, such as sharing, posting, commenting, or tagging",
                                 "How often do you visit or use Facebook?"),
                       stringsAsFactors = FALSE)
tab <- chisqTable("comm_facebook", "fb_freq", data = df2, varlabel = varlabel)
tab[c("table", "expected", "chisq.test")]
# plotTable("comm_facebook", "fb_freq", data = tab[["data.frame"]], varlabel = varlabel)
tab <- chisqTable("comm_facebook", "comm_inperson", data = df2, varlabel = varlabel)
tab[c("table", "expected", "chisq.test")]
tab <- chisqTable("fb_freq", "comm_inperson", data = df2, varlabel = varlabel)
tab[c("table", "expected", "chisq.test")]
```

```{r, warning = FALSE}
df2 <- 
  df0 %>% 
  mutate(comm_facebook = factor(comm_facebook,
                                levels = c("Several times a day",
                                           "Once a day",
                                           "A few times a week",
                                           "Once a week",
                                           "Every few weeks or less often"),
                                labels = c(rep("Daily or more", 2),
                                           rep("Less than daily", 3)))) %>%
                                # labels = LETTERS[1:5])) %>% 
  mutate(comm_inperson = factor(comm_inperson,
                                levels = c("Several times a day",
                                           "Once a day",
                                           "A few times a week",
                                           "Once a week",
                                           "Every few weeks or less often"),
                                # labels = c(rep("Daily or more", 2),
                                #            rep("Less than daily", 3)))) %>%
                                labels = LETTERS[1:5])) %>%
  mutate(comm_facebook = droplevels(comm_facebook),
         comm_inperson = droplevels(comm_inperson)) %>% 
  select(comm_facebook, comm_inperson)
varlabel <- data.frame(name = c("comm_inperson", "comm_facebook"),
                       label = c("Meet up in-person",
                                 "Actively interact on Facebook, such as sharing, posting, commenting, or tagging"),
                       stringsAsFactors = FALSE)
tab <- chisqTable("comm_inperson", "comm_facebook", data = df2, varlabel = varlabel)
tab[c("table", "expected", "residual", "chisq.test")]
mosaic(~ comm_inperson + comm_facebook, 
       data = df2, 
       shade = TRUE)
```

## FMSS items

Closely exam FMSS items 1, 2, 3, and 11

* `fmss_r1` For you, how good is Facebook for getting real help or support?
* `fmss_r2` For the support you get on Facebook, how much practical help is it?
* `fmss_r3` How much does the support you get on Facebook make you feel better?
* `fmss_r11` How close to people does Facebook make you feel?

```{r, warning = FALSE}
varlabel <- data.frame(name = c("fmss_r1", "fmss_r2", "fmss_r3", "fmss_r11", "indPHQ", "indDSISS"),
                       label = c("For you, how good is Facebook for getting real help or support?",
                                 "For the support you get on Facebook, how much practical help is it?",
                                 "How much does the support you get on Facebook make you feel better?",
                                 "How close to people does Facebook make you feel?",
                                 "PHQ-2 score greater than or equal to 3",
                                 "DSI-SS score greater than or equal to 2"),
                       stringsAsFactors = FALSE)
tab <- chisqTable("indPHQ", "fmss_r1", varlabel = varlabel)
tab[c("table", "expected", "chisq.test")]
tab <- chisqTable("indPHQ", "fmss_r2", varlabel = varlabel)
tab[c("table", "expected", "chisq.test")]
tab <- chisqTable("indPHQ", "fmss_r3", varlabel = varlabel)
tab[c("table", "expected", "chisq.test")]
tab <- chisqTable("indPHQ", "fmss_r11", varlabel = varlabel)
tab[c("table", "expected", "chisq.test")]
tab <- chisqTable("indDSISS", "fmss_r1", varlabel = varlabel)
tab[c("table", "expected", "chisq.test")]
tab <- chisqTable("indDSISS", "fmss_r2", varlabel = varlabel)
tab[c("table", "expected", "chisq.test")]
tab <- chisqTable("indDSISS", "fmss_r3", varlabel = varlabel)
tab[c("table", "expected", "chisq.test")]
tab <- chisqTable("indDSISS", "fmss_r11", varlabel = varlabel)
tab[c("table", "expected", "chisq.test")]
```

```{r}
x <- "fmssSubscore"
```


### PHQ-2

```{r}
y <- "indPHQ"
M0 <- fitModel(df1, y, x)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df1, y, x, covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```


### DSI-SS

```{r}
y <- "indDSISS"
M0 <- fitModel(df1, y, x)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df1, y, x, covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```


## FMSS quartiles

Stratify by FMSS quartile and compare Q1 vs Q4.

```{r, warning = FALSE}
varlabel <- data.frame(name = c("fmssQuartile", "indPHQ", "indDSISS"),
                       label = c("FMSS quartile",
                                 "PHQ-2 score greater than or equal to 3",
                                 "DSI-SS score greater than or equal to 2"),
                       stringsAsFactors = FALSE)
df3 <-
  df0 %>% 
  filter(grepl("Q[14]", fmssQuartile)) %>% 
  mutate(fmssQuartile = droplevels(fmssQuartile))
chisqTable("indPHQ", "fmssQuartile", data = df3, varlabel = varlabel)[c("table", "expected", "chisq.test")]
chisqTable("indDSISS", "fmssQuartile", data = df3, varlabel = varlabel)[c("table", "expected", "chisq.test")]
```

```{r}
x <- "fmssQuartile"
```


### PHQ-2

```{r}
y <- "indPHQ"
M0 <- fitModel(df3, y, x)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df3, y, x, covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```


### DSI-SS

```{r}
y <- "indDSISS"
M0 <- fitModel(df3, y, x)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(df3, y, x, covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```
