# Research Question 2

Are certains features of social media use are associated with positive screens for psychiatric disorders or a positive screen for suicidality?

* Spending more time on Facebook?
  * Frequency of Facebook use: `fb_freq`
  * Active use of Facebook: `comm_facebook`
* Sharing more personal or health-related information on social media?
  * `sm_emot_support`
  * `sm_med_info`
  * `sm_med_advice`
  * `sm_med_questions`
  * `sm_share_symptoms`
  * `sm_share_health`
  * `sm_share_suicide`
  
  
## Association between frequency of Facebook use and active use of Facebook

```{r}
df %>% select(fb_freq, comm_facebook) %>% na.omit() %>% cor %>% kable(digits = 3)
```


## Unadjusted comparisons

```{r}
align <- "lcccc"
digits <- c(0, 0, 0, 0, 3)
freq2Group("fb_freq", "indPTSD") %>% kable(align = align, digits = digits)
```

\newline

```{r}
freq2Group("comm_facebook", "indPTSD") %>% kable(align = align, digits = digits)
```

\newline

```{r}
freq2Group("fb_freq", "indPHQ") %>% kable(align = align, digits = digits)
```

\newline

```{r}
freq2Group("comm_facebook", "indPHQ") %>% kable(align = align, digits = digits)
```

\newline

```{r}
freq2Group("fb_freq", "indAuditC") %>% kable(align = align, digits = digits)
```

\newline

```{r}
freq2Group("comm_facebook", "indAuditC") %>% kable(align = align, digits = digits)
```

\newline

```{r}
freq2Group("fb_freq", "indDSISS") %>% kable(align = align, digits = digits)
```

\newline

```{r}
freq2Group("comm_facebook", "indDSISS") %>% kable(align = align, digits = digits)
```

\newline

```{r plot2Groups}
df %>% 
  melt(id.vars = c("record_id", "fb_freq"),
       measure.vars = c("indPTSD", "indPHQ", "indAuditC", "indDSISS")) %>% 
  filter(!is.na(value) & !is.na(fb_freq)) %>% 
  mutate(variable = case_when(variable == "indPTSD" ~ "PC-PTSD",
                              variable == "indPHQ" ~ "PHQ-2",
                              variable == "indAuditC" ~ "AUDIT-C",
                              variable == "indDSISS" ~ "DSI-SS")) %>% 
  mutate(variable = factor(variable, levels = c("PC-PTSD", "PHQ-2", "AUDIT-C", "DSI-SS"))) %>% 
  mutate(value = factor(value, levels = c(FALSE, TRUE), labels = c("Negative", "Positive"))) %>% 
  mutate(fb_freq = factor(fb_freq)) %>% 
  ggplot() +
  aes(x = fb_freq, color = value, fill = value) +
  geom_bar(data = . %>% filter(value == "Negative"), aes(y = ..count.. * (-1)), alpha = 1/1) +
  geom_bar(data = . %>% filter(value == "Positive"), alpha = 1/1) +
  scale_x_discrete("Frequency of Facebook use") +
  scale_y_continuous("Count", breaks = seq(-300, 300, 100), labels = abs(seq(-300, 300, 100))) +
  scale_color_brewer("Screened", palette = "Set1") + 
  scale_fill_brewer("Screened", palette = "Set1") + 
  facet_wrap(~ variable)
```

```{r plot2Groups}
df %>% 
  melt(id.vars = c("record_id", "comm_facebook"),
       measure.vars = c("indPTSD", "indPHQ", "indAuditC", "indDSISS")) %>% 
  filter(!is.na(value) & !is.na(comm_facebook)) %>% 
  mutate(variable = case_when(variable == "indPTSD" ~ "PC-PTSD",
                              variable == "indPHQ" ~ "PHQ-2",
                              variable == "indAuditC" ~ "AUDIT-C",
                              variable == "indDSISS" ~ "DSI-SS")) %>% 
  mutate(variable = factor(variable, levels = c("PC-PTSD", "PHQ-2", "AUDIT-C", "DSI-SS"))) %>% 
  mutate(value = factor(value, levels = c(FALSE, TRUE), labels = c("Negative", "Positive"))) %>% 
  mutate(comm_facebook = factor(comm_facebook)) %>% 
  ggplot() +
  aes(x = comm_facebook, color = value, fill = value) +
  geom_bar(data = . %>% filter(value == "Negative"), aes(y = ..count.. * (-1)), alpha = 1/1) +
  geom_bar(data = . %>% filter(value == "Positive"), alpha = 1/1) +
  scale_x_discrete("Active use of Facebook") +
  scale_y_continuous("Count", breaks = seq(-300, 300, 100), labels = abs(seq(-300, 300, 100))) +
  scale_color_brewer("Screened", palette = "Set1") + 
  scale_fill_brewer("Screened", palette = "Set1") + 
  facet_wrap(~ variable)
```


## Adjusted comparisons

```{r}
x <- "fb_freq"
covar <- c("countSocialMediaExclFB",
           "comm_inperson",
           "indSuicideConsideredEver",
           "countSuicideAttempts")
```

Filter subjects with missing covariates.

```{r}
df <-
  df %>% 
  select_(.dots = c("record_id", covar)) %>% 
  na.omit() %>% 
  select(record_id) %>% 
  merge(., df, by = "record_id")
```

Mutate independent variables to factors.

```{r}
df <-
  df %>% 
  mutate(fb_freq = factor(fb_freq),
         comm_facebook = factor(comm_facebook))
```


**TO-DO: Global hypothesis test of $beta_1, \ldots, beta_k$**


### PC-PTSD

```{r}
y <- "indPTSD"
M0 <- fitModel(y, x)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(y, x, covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```


### PHQ-2

```{r}
y <- "indPHQ"
M0 <- fitModel(y, x)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(y, x, covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```


### AUDIT-C

```{r}
y <- "indAuditC"
M0 <- fitModel(y, x)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(y, x, covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```


### DSI-SS

```{r}
y <- "indDSISS"
M0 <- fitModel(y, x)
table0 <- M0[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Unadjusted") %>% select(model, everything())
M <- fitModel(y, x, covar)
table1 <- M[["modelObject"]] %>% tidy(exponentiate = TRUE) %>% mutate(model = "Adjusted") %>% select(model, everything())
bind_rows(table0, table1) %>% rename(oddsratio = estimate) %>% kable(digits = 3)
```

\newline

```{r}
bind_rows(M0[["modelObject"]] %>% glance() %>% mutate(model = "Unadjusted") %>% select(model, everything()),
          M[["modelObject"]] %>% glance() %>% mutate(model = "Adjusted") %>% select(model, everything())) %>% 
  kable(digits = 3)
```
