# Read data

**Use only the REDCap survey data**

Notes on the REDCap identifier variables:

* If `[consent] == 1`, they started the eligibility survey; 
  * if `== 0` or `== NA`, they didn't.
* If `[consent_and_eligibility_complete] == 2`, they finished the screener (whether eligible or ineligible); 
  * if `== 0`, they dropped out or never started.
* If `[eligible] == 1`, they completed the screener and were eligible; 
  * if `== 0`, they completed and were ineligible;
  * if `== NA` , they dropped out or never started.
* If `[veterans_and_social_media_use_co] == 2`, they finished the survey; 
  * if `== 0`, they dropped out or never started (this includes people who were ineligible or didn't consent).
* If `[analytic_sample] == 0`, they completed the survey but were disqualified for data quality reasons; 
  * if `== 1`, they completed survey and was not disqualified for data quality reasons;
  * if `== NA`, they didn't complete the survey.

```{r}
df <-
  "C:/Users/chanb/Box Sync/Facebook pilot - Statisticians/REDCap dataset.csv" %>% 
  read.csv(stringsAsFactors = FALSE)
df %>% 
  group_by(consent, 
           consent_and_eligibility_complete, 
           eligible, 
           veterans_and_social_media_use_co, 
           analytic_sample) %>% 
  summarize(n = n()) %>% 
  kable
```

Inclusion criteria

* Respondents who consented
* Eligible, ineligible, or missing eligibility indicator

**`r sprintf("Number included: n = %d", df %>% filter(consent == 1) %>% nrow)`**

Cleaning

* Parse out `fba` into 2 separate variables for `image` and `text`
* Assign indicator for survey participation, `indSurveyParticipation`
  * `analytic_sample == 1`: Participant completed survey and was not disqualified for data quality reasons
* Assign indicator for eligibility screener participation, `indScreenerParticipation`
  * `eligible == 1`: Participant completed eligibility screener and was eligible to participate in full survey

```{r}
df <-
  df %>% 
  filter(consent == 1) %>% 
  mutate(image = 
           substr(fba, 1, 1) %>%
           factor(levels = c("c", "f", "v"),
                  labels = c("Computer", "Family", "Veteran")),
         text = 
           substr(fba, 2, 4) %>% 
           factor(levels = c("inc", "alt", "emp", "sha", "soc"),
                  labels = c("Incentive", "Altruism", "Empowerment", "Sharing", "SocialNorms"))) %>% 
  mutate(indSurveyParticipation = case_when(is.na(.$analytic_sample) ~ FALSE,
                                            .$analytic_sample == 1 ~ TRUE, 
                                            TRUE ~ FALSE)) %>%
  mutate(indScreenerParticipation = case_when(is.na(.$eligible) ~ FALSE,
                                              .$eligible == 1 ~ TRUE,
                                              TRUE ~ FALSE))
df %>% 
  group_by(image, text) %>% 
  summarize(n = n()) %>% 
  kable
df %>% 
  group_by(analytic_sample, indSurveyParticipation) %>% 
  summarize(n = n()) %>% 
  kable
df %>% 
  group_by(eligible, indScreenerParticipation) %>% 
  summarize(n = n()) %>% 
  kable
df %>% 
  group_by(indSurveyParticipation, indScreenerParticipation) %>% 
  summarize(n = n()) %>% 
  kable
```

## Use of VA health services

```{r}
df %>% 
  mutate(desc = "Before recoding") %>% 
  group_by(desc, va_ever_enrolled, va_use_12mo) %>% 
  summarize(n = n()) %>% 
  kable
```

Recoding logic

* Primary analysis will code `9` (not sure) as `0` (No)
* Sensitivity analysis will exclude the `9` values from the analysis
* If `va_ever_enrolled == FALSE` & `is.na(va_use_12mo)`, then recode `va_use_12mo` to `FALSE`
* If `va_use_12mo == TRUE` & `va_ever_enrolled == FALSE`, then recode `va_ever_enrolled` to `TRUE`
* Code indicators `indVANeverEnrolled` and `indVANotUse12mo` as the logical opposites of `va_ever_enrolled` and `va_use_12mo`

```{r}
df <-
  df %>%
  mutate(va_ever_enrolled = case_when(is.na(.$va_ever_enrolled) ~ NA,
                                      .$va_ever_enrolled == 9 ~ FALSE, 
                                      TRUE ~ as.logical(.$va_ever_enrolled))) %>%
  mutate(va_use_12mo = case_when(is.na(.$va_use_12mo) ~ NA,
                                 .$va_use_12mo == 9 ~ FALSE, 
                                 TRUE ~ as.logical(.$va_use_12mo)))
weirdRows <- which(df$va_ever_enrolled == FALSE & is.na(df$va_use_12mo))
df <- 
  df %>% 
  mutate(va_use_12mo = case_when(is.na(.$va_ever_enrolled) & is.na(.$va_use_12mo) ~ NA,
                                 row_number() %in% weirdRows ~ FALSE,
                                 TRUE ~ .$va_use_12mo))
weirdRows <- which(df$va_ever_enrolled == FALSE & df$va_use_12mo == TRUE)
df <- 
  df %>% 
  mutate(va_ever_enrolled = case_when(is.na(.$va_ever_enrolled) & is.na(.$va_use_12mo) ~ NA,
                                      row_number() %in% weirdRows ~ TRUE,
                                      TRUE ~ .$va_ever_enrolled))
df <-
  df %>%
  mutate(indVANeverEnrolled = !va_ever_enrolled,
         indVANotUse12mo = !va_use_12mo)
df %>% 
  mutate(desc = "After recoding") %>% 
  group_by(desc, va_ever_enrolled, va_use_12mo, indVANeverEnrolled, indVANotUse12mo) %>%
  summarize(n = n()) %>% 
  kable
```


## Independent variables

* Score the Modified Facebook Measure of Social Support (FMSS)
  * Reverse-scored items are `fmss_r7` through `fmss_r10`

```{r}
df <- 
  df %>%
  mutate(fmss = fmss_r1 +
                fmss_r2 +
                fmss_r3 +
                fmss_r4 +
                fmss_r5 +
                fmss_r6 +
                (4 - fmss_r7) +
                (4 - fmss_r8) +
                (4 - fmss_r9) +
                (4 - fmss_r10) +
                fmss_r11 +
                fmss_r12 +
                fmss_r13 +
                fmss_r14)
```

Check.

```{r histogramFMSS}
df %>% 
  filter(!is.na(fmss)) %>% 
  ggplot() + 
    aes(x = fmss) + 
    geom_histogram(binwidth = 1, alpha = 1/2) + 
    scale_x_continuous("FMSS") + 
    scale_y_continuous("Count")
```


## Psychiatric symptoms

Code indicators for psychiatric disorder screening scales

* PTSD
  * Name of scale: PC-PTSD 
  * Positive screen: `ptsd_intrusive` + `ptsd_avoidant` + `ptsd_guarded` + `ptsd_numb` + `ptsd_guilty` $\ge$ 3
* Major depression
  * Name of scale: PHQ-2
  * Positive screen: `phq_interest` + `phq_mood` $\ge$ 3
* Alcohol misuse
  * Name of scale: AUDIT-C
  * Positive screen: `auditc_freq` + `auditc_amount` + `auditc_binge` $\ge$ 4 for men, $\ge$ 3 for women

Presence of suicidality is defined as DSI-SS score $\ge$ 2.
This cut-off score was chosen based on recommendations for population-based samples noted in 
[von Glischinski M Clin Psychol Psychotherapy 2015](http://onlinelibrary.wiley.com/doi/10.1002/cpp.2007/full)

* Score the DSI-SS inventory
  * See [Joiner 2002](http://www.sciencedirect.com/science/article/pii/S0005796701000171)
  * *Scores on each item range from 0 to 3 and, for the inventory, from 0 to 12, with higher scores reflecting greater severity of suicidal ideation.*

```{r}
df <-
  df %>%
  mutate(ptsd = ptsd_intrusive + ptsd_avoidant + ptsd_guarded + ptsd_numb + ptsd_guilty) %>%
  mutate(indPTSD = ptsd >= 3) %>%
  mutate(phq = phq_interest + phq_mood) %>%
  mutate(indPHQ = phq >= 3) %>%
  mutate(auditc = auditc_freq + auditc_amount + auditc_binge) %>%
  mutate(indAuditC = case_when(
                       !is.na(gender) & gender == 1 ~ auditc >= 4,
                       !is.na(gender) & gender == 2 ~ auditc >= 3,
                       TRUE ~ NA)) %>% 
  mutate(dsiss = dsiss_thoughts + dsiss_plans + dsiss_control + dsiss_impulses) %>%
  mutate(indDSISS = dsiss >= 2)
```

Check.

```{r}
align <- "llccccc"
digits <- c(0, 0, 1, 0, 0, 0, 0)
means2Group("ptsd", "indPTSD") %>% kable(align = align, digits = digits)
means2Group("phq", "indPHQ") %>% kable(align = align, digits = digits)
means2Group("auditc", "indAuditC") %>% kable(align = align, digits = digits)
means2Group("dsiss", "indDSISS") %>% kable(align = align, digits = digits)
```
